%-------------------------
% Resume in Latex
% Author : Swapnaneel Patra
% Based off of: https://github.com/sb2nov/resume, Jake's Resume (Jake Gutierrez)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
\usepackage{mathptmx}
% \usepackage{newtxtext}
% \usepackage{txfonts}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\textit{\small#3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----------HEADER-----------
\begin{center}
  \textbf{\Huge SWAPNANEEL PATRA} \\ \vspace{1pt}
  \small +91 9547106242 $|$
  \href{mailto:swapnaneel_pa2503mth403@iitp.ac.in}{\underline{swapnaneel\_pa2503mth403@iitp.ac.in}} $|$
  \href{https://linkedin.com/in/swapnaneelpatra}{\underline{linkedin.com/in/swapnaneelpatra}} $|$
  \href{https://github.com/thisisrick25}{\underline{github.com/thisisrick25}}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institutes of Technology (IIT)}
{Patna, India}
{Master of Technology in Artificial Intelligence \& Data Science Engineering}
{Aug. 2025 -- Present}
\resumeSubheading
{Kalinga Institute of Industrial Technology (KIIT)}
{Bhubaneswar, India}
{Bachelor of Technology in Computer Science and Engineering}
{June 2019 -- Aug. 2023}
\resumeItemListStart
\resumeItem{GPA 8.38/10.0}
\resumeItem{\textbf{Coursework:} Data Structures and Algorithms, Design and Analysis of Algorithms, Machine Learning, Artificial Intelligence, Probability and Statistics, Operating Systems}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{Junior Software Engineer}{May 2024 -- Sep. 2024}
{EPAM Systems}{Hyderabad, India}
\resumeItemListStart
\resumeItem{Collaborated within an Agile team to deliver a scalable e-commerce web application, implementing CI/CD pipelines for iteration.}
\resumeItem{Designed secure user authentication and role-based access control (RBAC), enhancing data privacy and platform security.}
\resumeItem{Developed a dynamic product catalog with advanced search and filtering, improving user engagement and product discoverability.}
\resumeItem{Built an admin module for streamlined management of user access, orders, and product listings.}
\resumeItem{Created vendor tools for efficient product listing management and supplier onboarding.}
\resumeItemListEnd

\resumeSubheading
{Software Engineering Intern}{Jan. 2022 -- Apr. 2022}
{HighRadius Corporation}{Bhubaneswar, India}
\resumeItemListStart
\resumeItem{Collaborated on building a B2B invoice management system to streamline payment predictions and improve operational efficiency.}
\resumeItem{Built and trained a machine learning model, achieving 90.43\% accuracy in forecasting payment periods for B2B companies.}
\resumeItem{Streamlined backend data retrieval using servlets and the MVC design pattern, ensuring a responsive and user-friendly interface.}
\resumeItem{Created an intuitive Receivables Dashboard with structured grid visualization, making data more accessible and actionable.}
\resumeItem{Implemented robust CRUD functionalities and seamless pagination, enhancing navigation and data management for users.}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
% \resumeSubSubheading
%   {Software Engineer I}{Oct 2014 - Sep 2016}
%   \resumeItemListStart
%     \resumeItem{Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%   \resumeItemListEnd
% -------------------------------------------

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
\resumeItemListStart
\resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
\resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
\resumeItem{Visualized GitHub data to show collaboration}
\resumeItem{Used Celery and Redis for asynchronous tasks}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
\resumeItemListStart
\resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
\resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
\resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
\resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
\resumeItemListEnd
\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
        \textbf{Languages}{: Python, C/C++, SQL (Postgres), JavaScript, TypeScript, HTML/CSS} \\
        \textbf{Frameworks}{: React, Next.js, Node.js, JUnit, FastAPI} \\
        \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
        % \textbf{Libraries}{: pandas, NumPy, Matplotlib}
        }}
\end{itemize}


%-------------------------------------------
\end{document}